### 2025-04-05 sports-cognitive-psychology.qmd
20250405 - video citation

For instance, here is a 2016 video clip of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops", suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.

![Football Commentator Making Fun of Analytics in Football. From: <https://streamable.com/1hw8> (2016).](images/commentatorOnAnalytics.mp4){width=100%}\

@@

Nevertheless, more and more people around the league are using analytics—likely because it works; for examples of articles, see [here](https://www.theringer.com/2018/12/19/nfl/nfl-analytics-revolution) [@Clark2018; archived at <https://perma.cc/7BKP-A4GJ>] and [here](https://www.samford.edu/sports-analytics/fans/2020/The-Future-of-NFL-Data-Analytics) [@Awbrey2020; archived at <https://perma.cc/WXE3-53E6>].
Head Coach Doug Peterson heavily relied on analytics with the Philadelphia Eagles to help them win the 2017 Super Bowl; for more information, see [here](https://www.forbes.com/sites/liamfox/2021/08/12/how-the-nfl-uses-analytics-according-to-the-lead-analyst-of-a-super-bowl-champion/) [@Fox2021; archived at <https://perma.cc/49KQ-R785>] and [here](https://www.nfl.com/news/super-bowl-lii-how-the-2017-philadelphia-eagles-were-built-0ap3000000912753) [@Rosenthal2018; archived at <https://perma.cc/2GRF-8Z5K>].

>>>>

For instance, here is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" [@ABC2015], suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

![Football Commentator Making Fun of Analytics in Football. From: <https://streamable.com/1hw8> (2015).](images/commentatorOnAnalytics.mp4){width=100%}\

@@

Nevertheless, more and more people around the league use analytics—likely because it works; for examples of articles, see [here](https://www.theringer.com/2018/12/19/nfl/nfl-analytics-revolution) [@Clark2018; archived at <https://perma.cc/7BKP-A4GJ>] and [here](https://www.samford.edu/sports-analytics/fans/2020/The-Future-of-NFL-Data-Analytics) [@Awbrey2020; archived at <https://perma.cc/WXE3-53E6>].
Head Coach Doug Peterson heavily relied on analytics with the Philadelphia Eagles to help them win the 2017 Super Bowl; for more information, see [here](https://www.forbes.com/sites/liamfox/2021/08/12/how-the-nfl-uses-analytics-according-to-the-lead-analyst-of-a-super-bowl-champion/) [@Fox2021; archived at <https://perma.cc/49KQ-R785>] and [here](https://www.nfl.com/news/super-bowl-lii-how-the-2017-philadelphia-eagles-were-built-0ap3000000912753) [@Rosenthal2018; archived at <https://perma.cc/2GRF-8Z5K>].
